SFJ: An implementation of Semantic Featherweight Java

### 2020-02-28 conference/paper.tex
minor

In this paper, we present SFJ---Semantic Featherweight Java, an implementation of FJ which features boolean types and structural subtyping as well as nominal subtyping.
The benefits of SFJ, also illustrated in the accompanying video \cite{UD20}, show how static typechecking of boolean types and semantic subtyping gives higher guarantees of program correctness, more flexibility and compactness of program writing.
%\keywords{Nominal subtyping \and Structural subtyping  \and Semantic Featherweight Java \and Object-oriented languages \and Boolean types \and Type theory.}
\end{abstract}

>>>>

In this paper, we present SFJ---Semantic Featherweight Java, an implementation of FJ which features boolean types and structural subtyping as well as nominal subtyping.
The benefits of SFJ, illustrated in the paper and the video (with audio/subtitles) \cite{UD20}, show how static typechecking of boolean types and semantic subtyping gives higher guarantees of program correctness, more flexibility and compactness of program writing.
%\keywords{Nominal subtyping \and Structural subtyping  \and Semantic Featherweight Java \and Object-oriented languages \and Boolean types \and Type theory.}
\end{abstract}
